Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-09-22 ms.tex
added time series and allan variance for GL dewar Run 112

>>>>

\subsection{Run 112}
We also investigate a slightly longer time series for GL dewar.

\begin{figure*}
\gridline{\fig{azlab_ratio_tser_gldewar_run112_sub4_hi4_no_backsub.pdf}{0.48\textwidth}{Time series for S01 / S02 Ratio No Background Sub}
\fig{azlab_ratio_tser_gldewar_run112_sub4_hi4.pdf}{0.48\textwidth}{Time series for S01 / S02 Ratio With Background Sub}}
\caption{Time series for rectangular photometry on the S01 and S02 detectors as well as background-subtracted Rectangular photometry}}\label{fig:GLtSeriesRun112}
\end{figure*}

\begin{figure*}
\gridline{\fig{all_var_gl_dewar_run112_sub4_hi4_no_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram no background subtraction}
\fig{all_var_gl_dewar_run112_sub4_hi4_with_backsub_removelinear_False_2.pdf}{0.48\textwidth}{Allan variance diagram with background subtraction}}
\caption{Time series for background-subtracted rectangular photometry on the S02 and S03 detectors.
The ratio of the two detectors' fluxes, after background subtraction, scales like $\sqrt{N}$ statistics down to the 200 ppm level, but how it works on longer timescales is not yet known.}\label{fig:GLtSeriesAcrossDetectors}
\end{figure*}
